Prefetching SPARQL query cacher

### 2016-07-28 dissertation/cache-proxy.tex
add simple example

>>>>

The resulting plan trees may be represented as strings as follows:
\begin{example}{Four Attean plan trees}
\begin{verbatim}
- Hash Join { s } (distinct cost: 27)
-   Quad { ?s, <http://example.org/p>, ?o, <http://example.org/> } (cost: 15)
-   Quad { ?s, <http://example.org/p>, "1", <http://example.org/> } (cost: 12)

- Hash Join { s } (distinct cost: 28)
-   Quad { ?s, <http://example.org/p>, "1", <http://example.org/> } (cost: 12)
-   Quad { ?s, <http://example.org/p>, ?o, <http://example.org/> } (cost: 15)

- NestedLoop Join (distinct cost: 180)
-   Quad { ?s, <http://example.org/p>, "1", <http://example.org/> } (cost: 12)
-   Quad { ?s, <http://example.org/p>, ?o, <http://example.org/> } (cost: 15)

- NestedLoop Join (distinct cost: 180)
-   Quad { ?s, <http://example.org/p>, ?o, <http://example.org/> } (cost: 15)
-   Quad { ?s, <http://example.org/p>, "1", <http://example.org/> } (cost: 12)
\end{verbatim}
\end{example}
In the above example, the first plan tree will be returned from the
query planner for execution, since it has the lowest estimated cost
(27).
